%----------------------------------------------------------------------------------------
%	Executive Summary
%----------------------------------------------------------------------------------------

\chapter{Executive Summary}

The project involves designing and developing a scale system that automates the processing of weight data for dogs at SPCA. The final product should speed up the weighing process, allowing staff to work more efficiently and focus more on the animal's health and care.

The project includes both hardware and software components. The hardware component focuses on implementing the actual scale that is used to weigh the dogs and providing the analogue data while the software component focuses on processing that data and developing a web platform that SPCA staff can use for easy data management.

In the hardware section, the operating principles as well as the proposed circuit design to detect and measure the weight is discussed. This includes the incorporation of a Wheatstone bridge and operational amplifiers as well as filters to stabilize and clean the output signal. This will be integrated with the Raspberry Pico W and other various components such as LEDs and buttons for functionality. 

In the software section, the embedded implementation, back-end, and front-end is discussed. The embedded design covers the utilization of the Raspberry Pico W module to receive analogue inputs from the scale, process this data, and transmit the processed data via  WiFi module to the back-end. A state machine design is proposed to keep track of all data inputs and outputs. The back-end section covers  the technologies used for the database and user authentication. It also includes a list of the exposed endpoints and its use case. The front-end section covers technologies used to develop the web platform and includes the different functionalities that will be provided by the platform. Possible user flows are suggested and the actual prototype for the web platform can be found in the Appendices.

Along with the proposed design solution, we have also considered the cultural, environmental, legal and ethical impacts. This includes the consideration of the Te Tiriti o Waitangi, especially the aspect of data sovereignty and its importance. We also looked at the sustainability and environmental impacts of our solution - namely resource procurement, energy consumption, product durability and recyclability. Another important aspect was legal and privacy concerns such as data collection and related disclosures.