%----------------------------------------------------------------------------------------
%	Technical Overview
%----------------------------------------------------------------------------------------

\chapter{Technical Overview}

% TODO: Provide a technical overview of the whole project
\par Our team has decided to divide roles into three distinct sections: hardware, embedded software and software. We have assigned each team member according to their specialisations. By dividing our roles in this way, we hope to maximise efficiency and productivity while also ensuring that each team member can utilise their unique skill set. 

The hardware section will be responsible for designing, building and maintaining the physical components of the project, such as circuit boards and sensors. The embedded software section will be responsible for programming the micro-controllers and other embedded systems that control the functionality of the hardware. The software section will be responsible for developing the applications that will interact with the hardware, as well as the user interfaces. Although each team member has been assigned to a specific section, we will work together in coordination. We will support each other when help is needed, and prioritize good communication within the team.

To plan the overall project, we have utilised a Gantt chart. This tool allows us to visualise the project timeline and identify important tasks. By breaking down the project into manageable tasks and assigning deadlines, we can better track our progress and ensure that we stay on schedule. The Gantt chart will be a valuable resource in keeping our team organised and focused throughout the project. The Gantt chart can be found in Figure A.1.


